---
title: "amica QC Report"
date: '`r format(Sys.Date(), "%Y-%B-%d")`'
output: html_document
params:
  numberOfProteins: NA
  quantifiedProteins: NA
  numberOfComparisons: NA
  numberOfGroups: NA
  densityplot: NA
  numid: NA
  contaminants: NA
  missingvals: NA
  overlap: NA
  overlapDf: NA
---

## Analysis parameters 
```{r}
# The `params` object is available in the document.
params$nsubmits
params$numberOfProteins
params$quantifiedProteins
params$numberOfGroups
```


### Summary

There are 

| Tables   |      Are      |  Cool |
|----------|:-------------:|------:|
| Number of proteins |  `r params$numberOfProteins` | $1600 |
| col 2 is |    `r params$quantifiedProteins`   |   $12 |
| col 2 is |    `r params$numberOfGroups`   |   $12 |
| col 3 is | `r params$numberOfComparisons` |    $1 |

### QC plots

#### Number of identified proteins (based on LFQ intensities prior to imputation)
```{r}
params$numid
```

#### Percentages of contamination (based on iBAQ intensities)
```{r}
params$contaminants
```

#### Percentages of missing values (based on LFQ intensities prior to imputation)
```{r}
params$missingvals
```


#### Overlap table
```{r}
params$overlap
df <- params$overlapDf
names(df) <- c(
      "Sample 1",
      "Sample 2",
      "# Sample 1",
      "# Sample 2",
      "# shared",
      "Overlap Coeff.",
      "Jaccard index"
    )
    datatable(
      df,
      extensions = 'Buttons',
      filter = "top",
      rownames = F,
      options = list(
        pageLength = 10,
        autoWidth = TRUE
        #dom = 'Bfrtip',
        #buttons = c('csv')
      )
    )
```


